% Develop a LaTeX script to create a document that consists of two paragraphs with a minimum of 10 citations in it and display the reference in the section

\documentclass{article}
\usepackage[numbers]{natbib}  
\begin{document}
\title{Document that Consists of Two Paragraphs with a minimum of 10 Citations in it and Displaying the References in the Section}
\date{}
\maketitle
\paragraph{Paragraph 1}
The theory of relativity has been explored extensively in various scientific papers \citep{author1, author2}. Einstein's contributions to physics are profound and have paved the way for many modern discoveries \citep{author3}. Researchers continue to investigate the complexities of spacetime and the universe\citep{author4}. These advancements have led to new methods of measurement and analysis in cosmology \citep{author5}.
\paragraph{Paragraph 2}
Recent studies have focused on the impact of climate change on various ecosystems \citep{author6, author7}. Scientists are examining how rising temperatures and changing weather patterns affect biodiversity and human health \citep{author8}. Furthermore, interdisciplinary research has brought about innovative solutions for sustainable development \citep{author9}. Collaboration among experts from different fields is essential to address the challenges of global warming \citep{author10}.
\newpage 
\begin{thebibliography}{99}
    \bibitem{author1} Einstein A. \textit{" Relativity: The Special and General Theory"}. New York: H. Holt and Company, 1916.
    \bibitem{author2} Einstein, Albert. \textit{"Time, Space, and Gravitation"}. The Times, 28 November 1919.
     \bibitem{author3} Einstein, Albert. \textit{"Time, Space, and Gravitation"}. The Times, 28 November 1919.
    \bibitem{author4} Hey, Anthony J.G.; Walters, Patrick. \textit{"The New Quantum Universe"}. Cambridge University Press, p. 227, 2003.
    \bibitem{author5} Kennedy, R.J.; Thorndike, E.M. \textit{"Experimental Establishment of the Relativity of Time"}. Physical Review, pp. 400-418, 1932.
    \bibitem{author6} Lynas, Mark; Houlton, Benjamin Z.; Perry, Simon. \textit{"Greater than 99\% consensus on human caused climate change in the peer-reviewed scientific literature"}. Environmental Research Letters, 19 October 2021.
    \bibitem{author7} GISS Surface Temperature Analysis (v4). \textit{"NASA"}. Retrieved 12 January 2024.
    \bibitem{author8}  World Health Organization(WHO). \textit{"Connecting Global Priorities: Biodiversity and Human Health, a State of Knowledge Review".} 2015.
    \bibitem{author9} United Nations General Assembly. \textit{"Report of the World Commission on Environment and Development: Our Common Future"}. Transmitted to the General Assembly as an Annex to document A/42/427 – Development and International Co-operation: Environment., 1987.
    \bibitem{author10} Ivanova, Irina . \textit{"California is rationing water amid its worst drought in 1,200 years"}. CBS News, 2 June 2022.
\end{thebibliography}
\end{document}
